---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# kubrand

<!-- badges: start -->
[![Codecov test coverage](https://codecov.io/gh/bvancilku/kubrand/branch/main/graph/badge.svg)](https://codecov.io/gh/bvancilku/kubrand?branch=main)
[![R-CMD-check](https://github.com/bvancilku/kubrand/workflows/R-CMD-check/badge.svg)](https://github.com/bvancilku/kubrand/actions)
<!-- badges: end -->

The goal of kubrand is to simplify theming a ggplot2 graph using KU branded colors.

## Installation

<!--
You can install the released version of kubrand from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("kubrand")
```
-->

The development version of the package is available from [GitHub](https://github.com/) with:

``` r
# install.packages("remotes")
remotes::install_github("bvancilku/kubrand")
```

## Example

Make a plot using the KU-branded ggplot2 theme:

```{r example}
library(dplyr)
library(ggplot2)
library(magrittr)
library(purrr)

library(kubrand)
base::set.seed(2021L + 07L + 05L)
dataset <- tibble::tibble(
  val_x_true = base::seq(1, 100, by = 1)
) %>% 
  dplyr::mutate(
    val_x_measured = val_x_true + stats::rnorm(dplyr::n(), mean = 0, sd = 0.6),
    ind_treatment = purrr::rbernoulli(dplyr::n()),
    val_y_true = val_x_true * (1.1 + (1 - 0.4 * ind_treatment) * base::sin(val_x_true / 10)),
    val_y_measured = val_y_true + stats::rnorm(dplyr::n(), mean = 0, sd = 5),
    cat_treatment = base::factor(dplyr::if_else(ind_treatment, "treatment", "control"), levels = c("control", "treatment"))
  )

categorical_palette <- kubrand::ku_pal("cat2_int", reverse = TRUE)(2L)
dataset %>% 
  ggplot2::ggplot() +
  ggplot2::aes(x = val_x_measured, y = val_y_measured, color = cat_treatment, shape = cat_treatment) +
  ggplot2::geom_point(show.legend = FALSE) +
  ggplot2::xlab("x") +
  ggplot2::ylab("y") +
  kubrand::scale_color_ku("cat2_int", reverse = TRUE) +
  ggplot2::ggtitle(
    label = glue::glue("The **{kubrand::color_text(categorical_palette[[2]], 'treatment')}** attenuates oscillation relative to the **{kubrand::color_text(categorical_palette[[1]], 'control')}**"),
    subtitle = "Sometimes one needs a subtitle. This is not one of those times."
  ) +
  theme_ku()
```

## Code of conduct

Please note that the kubrand project is released with a [Contributor Code of Conduct](https://contributor-covenant.org/version/2/0/CODE_OF_CONDUCT.html). By contributing to this project, you agree to abide by its terms.

## Related work

This package relies on the hard work of other package maintainers as well as many good tutorials and articles. Please allow us to commend them here.

### Articles

- ["Creating corporate colour palettes for ggplot2" by Simon Jackson ](https://drsimonj.svbtle.com/creating-corporate-colour-palettes-for-ggplot2)
- ["Bivariate maps with ggplot2 and sf" by Timo Grossenbacher ](https://timogrossenbacher.ch/2019/04/bivariate-maps-with-ggplot2-and-sf/)
- ["Choosing color palettes for data visualization that are accessible for most audiences (useR! 2021) by Achim Zeileis"](https://www.youtube.com/watch?v=PstHyodalWg)

### Packages

- base R's {grDevices}. Much work has recently gone into `palette.colors()`/`palette.pals()` and `hcl.colors()`/`hcl.pals()`
- [bayesplot](https://cran.r-project.org/package=bayesplot)
- [biscale](https://cran.r-project.org/package=biscale)
- [colorspace](https://cran.r-project.org/package=colorspace)
- [dplyr](https://cran.r-project.org/package=dplyr)
- [extrafont](https://cran.r-project.org/package=extrafont)
- [farver](https://cran.r-project.org/package=farver)
- [ggplot2](https://cran.r-project.org/package=ggplot2)
- [ggtext](https://cran.r-project.org/package=ggtext)
- [glue](https://cran.r-project.org/package=glue)
- [magrittr](https://cran.r-project.org/package=magrittr)
- [methods](https://cran.r-project.org/package=methods)
- [paletteer](https://cran.r-project.org/package=paletteer)
- [pals](https://cran.r-project.org/package=pals)
- [patchwork](https://cran.r-project.org/package=patchwork)
- [purrr](https://cran.r-project.org/package=purrr)
- [ragg](https://cran.r-project.org/package=ragg) provides more modern graphics device replacements that work with {systemfonts} 
- [rcartocolor](https://cran.r-project.org/package=rcartocolor)
- [RColorBrewer](https://cran.r-project.org/package=RColorBrewer)
- [rlang](https://cran.r-project.org/package=rlang)
- [scales](https://cran.r-project.org/package=scales)
- [scico](https://cran.r-project.org/package=scico)
- [stringr](https://cran.r-project.org/package=stringr)
- [svglite](https://cran.r-project.org/package=svglite)
- [systemfonts](https://cran.r-project.org/package=systemfonts) allows one to specify font variants with specific font features; can be used in conjunction with {ragg}
- [unikn](https://cran.r-project.org/package=unikn) [unikn GitHub repo](https://github.com/hneth/unikn) is a university color palette with guidance on creating one's own palette.
- [viridis](https://cran.r-project.org/package=viridis)


### Tools

- <https://hclwizard.org/>
